Weather Data Integration and Assimilation System\\

### 2020-02-13 introduction/sec_2-problem_and_objectives.tex

\emph{....}
\dbc{Give a proper problem statement.}

>>>>

\emph{Design and implement an extendable weather data integration, assimilation and dissemination system which is capable of handling bulk data efficiently with providing scalability and high throughput with using open source tools and modern cloud computing technologies.}
\dbc{Give a proper problem statement.}
\gkc{UPDATED. Looked into the OneNote samples. I  should follow one of them from the beginning. :( }
